%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{xcolor}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{mathptmx}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\newcommand{\MYhref}[3][black]{\href{#2}{\color{#1}{#3}}}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{2.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    \textbf{\Huge \scshape Carlos Vega}
\end{center}

\begin{center}
\vspace{-.3cm}
\small +1 (917) 943-2594 $|$
\href{mailto:carlosvegalemus@gmail.com}{\underline{carlosvegalemus@gmail.com}} $|$
\href{https://www.linkedin.com/in/carlos-vega-lemus/}{\underline{linkedin.com/in/carlos-vega-lemus}} $|$
\href{https://github.com/iCarlosVega}{\underline{github.com/iCarlosVega}} $|$
\href{https://carlos-vega.co/}
{\underline{Personal Website}}
\end{center}
\vspace{-.6cm}

%----------Objective----------

%\section{Professional Summary}
%{Recent Computer Science and Mathematics graduate with hands-on experience in full-stack development. Proven experience building data intensive systems. Proficient in system design and eager to apply a data-driven, problem-solver mindset to enhance the technology in NYC.}
%---------------- experience--------

\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Mobot $|$ AI Cloud Robotics}{Jan. 2026 - Present}
      {Quality Assurance Analyst}{New York, NY}
      \resumeItemListStart
        \resumeItem{Developed and optimized comprehensive test plans for high-profile clients, including Chime, Doordash, and Citizen, ensuring quality standards and enhancing overall application reliability}
        \resumeItem{Executed and managed manual and automated tests for 20+ iOS and Android apps by leveraging Mobot's robots alongside Docker, Postman, and ADB commands, improving bug detection rates by 20\%}
        \resumeItem{Collaborated with a team of 10+ engineers, handling requests weekly via Jira and Slack, debugging JavaScript issues, and optimizing SQL databases as well as data pipelines.}
        \resumeItem{Implemented a cross-platform data integration feature within the React frontend, enabling instant retrieval of legacy test reports to streamline root-cause analysis for hardware failures.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  %-----------Tools-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
 \small{\item{
\textbf{Languages:} Python, JavaScript/TypeScript, SQL, Java, C\# \\
\textbf{Backend/Distributed Systems:} FastAPI, PostgreSQL, Redis, NoSQL, ASP.NET, Clickhouse \\
\textbf{Frontend:} React, Next.js, Tailwind \\
\textbf{AI/ML/Data:} Claude Code, Pandas, NumPy, Scikit-learn \\
\textbf{DevOps \& Cloud:} Railway, Docker, Supabase \\
\textbf{Tools \& Testing:} Git/GitHub, Pytest \\
\textbf{Spoken Languages:} English (Native), Spanish (Native)
}}
\end{itemize}


  %-----------Projects-----------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeSubheading
      {\textbf{Overtake.fyi} $|$ \normalfont\textit{Python, TypeScript, FastAPI, PostgreSQL, Next.js, ASP.NET, Clickhouse \MYhref[black]{https://www.overtake.fyi}{\faGithub}}}{June 2025 - Present}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Built an F1 telemetry analytics platform with a dual-database design: ClickHouse for \textasciitilde60M high-frequency telemetry records/season and PostgreSQL for relational race and standings data.}
        \resumeItem{Engineered an Python/FastF1 ETL pipeline ingesting per-driver lap telemetry (3,000 samples/lap × 20 drivers × 20+ races) into ClickHouse.}
        \resumeItem{Designed an async ASP.NET Core REST backend with parallel multi-driver telemetry queries and driver number aliasing to resolve cross-season number changes.}
        \resumeItem{Implemented client-side adaptive downsampling (bucket min-max, 100k+ → 4k points) with shareable URL state for all chart parameters.}
    \resumeItemListEnd

    \resumeSubheading
        {\textbf{Cognitus} $|$ \normalfont\textit{Python, TypeScript, FastAPI, LanceDB, Next.js, LangChain, LangGraph \MYhref[black]{https://github.com/iCarlosVega/Cognitus/}{\faGithub}}}{Present}
        {}{}
        \resumeItemListStart
        \vspace{-4mm}
            \resumeItem{Built an academic citation network visualizer with a dual-database architecture: SQLite for relational paper/workspace/edge data, and LanceDB for 768-dimensional vector embeddings.}
            \resumeItem{Built a fully local AI stack with a LangGraph ReAct agent that autonomously iterates over search and retrieval tools to surface foundational papers.}
            \resumeItem{Implemented a RAG pipeline where papers are embedded on ingestion and cosine similarity ($\geq$0.80) auto-generates semantic edges between thematically related papers; rendered on a React Flow canvas with custom node/edge type distinction.}
        \resumeItemListEnd

      \resumeSubheading
      {\textbf{AI Admissions Assistant} $|$ \normalfont\textit{Python, React, Flask, AzureAI Foundry}}{Oct. 2023}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Spearheaded the content acquisition for RAG by recursively web-scraping and processing over 500 unique pages, yielding a comprehensive dataset of 2023 information.}
        \resumeItem{Engineered a data processing pipeline to vectorize over 2GB of web-scraped text data, creating a secure and actionable knowledge base for a RAG system.}
        \resumeItem{Reduced outdated responses from the base LLM by approximately 65\% for inquiries requiring 2023 information}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CUNY Queens College}{Queens, NY}
      {Bachelor of Arts in Computer Science and Mathematics}{May 2025}
      \resumeItemListStart
      \resumeItem{\textbf{Google Software Engineering Program Fellow (G-SWEP):} Selected for a competitive program focused on Google's software engineering principles, technical interview preparation, and best practices in code development.}
          % Add more courses here
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%------ Professional Development -------
  \section{Professional Development}
  \resumeSubHeadingListStart
       \resumeSubheading
    {Founder, Custom 3D Printing Business}{Jan. 2025 - Present}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Managed end-to-end product lifecycle from client consultation and 3D design to printing and final delivery, completing a 200+ unit order for a major non-profit (Big Brothers Big Sisters of NYC).}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
